

########## Build setup #########################################################


================================================================================
1.  Download minimal basic project called "reference project" or "poky"

--------------------------------------------------------------------------------
1.1 For phytec download a script and run it in a new empty project folder:

    wget ftp://ftp.phytec.de/pub/Software/Linux/Yocto/Tools/phyLinux
    chmod +x phyLinux
    ./phyLinux init

    For more information see the phytec Manual
    https://www.phytec.de/documents/?title=l-813e-7-yocto-reference-manual#phyLinux


--------------------------------------------------------------------------------
1.2 For general use download the reference project poky directly

    git clone git://git.yoctoproject.org/poky


================================================================================
2.  Setup the build enviroment:

--------------------------------------------------------------------------------
2.1 Configure the following dictionary locations:

................................................................................
2.1.1 What?
    - deploy directory = each project should have its own deploy directory
                        where to put the compilation results.
    - sstate directory = The (temporary) building stats holding intermediate
                        files. This can be shared between multi project
    - download directory = This folder holds all files which were fetched
                            (downloaded) from the internet. This folder should
                            be globale to all project so that the files must
                            only downloaded once for all.


................................................................................
2.1.2 Where?
    But the following into your build/conf/local.conf file:
    - SSTATE_DIR = "<path/to/your/folder>"
    - DL_DIR = "<path/to/your/folder>"
    - DEPLOY_DIR = "<path/to/your/folder>"


--------------------------------------------------------------------------------
2.2 Source the configuration script into your current shell. It configures the
    build environment:

    soure poky/oe-init-build-env





================================================================================
3.0 Configure the build.

--------------------------------------------------------------------------------
3.1 Configuration files

................................................................................
3.2 Globle build files. Configuration for all meta-data and recipes

 (1) build/bblayers.conf    = Meta data layers to include into the build.
 (6) build/local.conf       = Global project specific configuration file.
 (4) build/site.conf        = Same like local.conf. But should encapsulate
                                the destination (site) access information like
                                proxy settings.
 (5) build/auto.conf        = Meta data layers to include into the build.

 p
................................................................................
3.2 meta-data recipies/layer dependet configuration/build files. 

 (2) source/meta-<yourMetaDataLayer>/conf/layer.conf     =
            Same like local.conf but only for this meta-layer.
 (7) source/meta-<yourMetaDataLayer>/conf/<machine>.conf =
            Configuration about the target (mcu, board,...).
 (8) source/meta-<yourMetaDataLayer>/conf/<distro>.conf  =
            Configuration to the target distribution to compile.

................................................................................
3.3 Bitbake configuration file

 (3) source/poky/meta/conf/bitbake.conf

................................................................................
3.4 Order in which the files gets include/parsed.

    The order is defined by the numbers above in 3.1 - 3.2. Depending on the
    assignment to the variables, the first (normal) or least one wins. For
    further information take a look into the bitbake syntax how to assign
    values to variables.








================================================================================
x.0 Default and Template configurations

--------------------------------------------------------------------------------
x. 1 When calling (sourcing) the oe-init-build-env script you can define some
    default/template configuration files for 'local.conf' and 'bblayer.conf'.
    To do so, set the folder where this local.conf.sample or bblayer.conf.sample
    file live to the enviroment variable "TEMPLATECONF" before sourcing the
    script oe-init-build-env script.

    export TEMPLATECONF=<mypath/folder>


